Management induced changes of soil organic carbon on global croplands

### 2020-12-14 ResultNotebooks/results_SOCflows.Rmd
Flow figure update

outputdir <- "Output/Images"
revfolder <- "Data/histManagement/"

@@

CarbonInput      <- readRDS(paste0(revfolder,"CarbonInput.rds"))[,year,]
CarbonLitter     <- readRDS(paste0(revfolder,"CarbonLitter.rds"))[,year,]
CarbonManure     <- readRDS(paste0(revfolder,"CarbonManure.rds"))[,year,]          
CarbonResidues   <- readRDS(paste0(revfolder,"CarbonResidues.rds"))[,year,]
CarbonHarvest    <- readRDS(paste0(revfolder,"Crop_Harvest.rds"))[,year,]
CarbonVegetation <- readRDS(paste0(revfolder,"CarbonVegetation.rds"))[,years,]
SoilCarbonOut    <- readRDS(paste0(revfolder,"SoilCarbon.rds"))[,years,]
CarbonInflow      <- readRDS(paste0(revfolder,"CarbonInflow.rds"))[,years,]

@@

TotalSOCBudget    <- mbind(TotalSOCBudget,
                           setNames(SOCsub[,,"natveg"], gsub("\\.","_",getNames(SOCsub))),
                           SOCtot)

CarbonIn          <- grepSpaceTime(SteadyState[,,"alpha_in"]*Landuse)

@@

```{r}
####### delete when new output on decay is ready
# Decay

ActiveDecay        <- mbind(setNames(calcOutput("ActiveDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("ActiveDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
SlowDecay          <- mbind(setNames(calcOutput("SlowDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("SlowDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
PassiveDecay       <- mbind(setNames(calcOutput("PassiveDecay", landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("PassiveDecay", landtype="natveg", aggregate = FALSE),"natveg"))
decay <- calcOutput("Decay", aggregate = FALSE)
subpools     <- c("active","slow","passive")
names        <- as.vector(outer(getNames(Landuse), subpools, paste, sep="."))
Decay <- new.magpie(getCells(Landuse), getYears(Landuse), names, fill = 0)

Decay[,,"active"]                  <- ActiveDecay
Decay[,,"slow"]                    <- SlowDecay
Decay[,,"passive"]                 <- PassiveDecay

rm(ActiveDecay, SlowDecay, PassiveDecay)

#
####### end delete

>>>>

outputdir <- "Output/"
revfolder <- "Data/histManagement/"

@@

CarbonInput      <- readRDS(paste0(revfolder,"CarbonInput.rds"))[,year,]
CarbonLitter     <- readRDS(paste0(revfolder,"CarbonLitter.rds"))[,year,]
CarbonManure     <- readRDS(paste0(revfolder,"CarbonManure.rds"))[,year,]          
CarbonResidues   <- readRDS(paste0(revfolder,"CarbonResidues.rds"))[,year,]
CarbonHarvest    <- readRDS(paste0(revfolder,"Crop_Harvest.rds"))[,year,]
CarbonVegetation <- readRDS(paste0(revfolder,"CarbonVegetation.rds"))[,years,]
SoilCarbonOut    <- readRDS(paste0(revfolder,"SoilCarbon.rds"))[,years,]
CarbonInflow     <- readRDS(paste0(revfolder,"CarbonInflow.rds"))[,years,]
CarbonDecay      <- readRDS(paste0(revfolder,"Decay.rds"))[,year,]

@@

TotalSOCBudget    <- mbind(TotalSOCBudget,
                           setNames(SOCsub, gsub("\\.","_", getNames(SOCsub))),
                           setNames(SOCtot, paste0("soc_", getNames(SOCtot))))

CarbonIn          <- grepSpaceTime(CarbonInflow[,,"crop"]*Landuse[,,"crop"])
CarbonIn          <- mbind(CarbonIn[,,"ag"],CarbonIn[,,"bg"],
                           add_dimension(dimSums(
                             CarbonIn[,,c("livst_chick","livst_egg","livst_milk","livst_pig","livst_rum")], dim=3.1),
                              add="subpool", nm="manure"))

TotalSOCBudget    <- mbind(TotalSOCBudget,
                           setNames(CarbonIn, gsub("\\.","_", getNames(CarbonIn))))
CarbonInTot       <- dimSums(CarbonIn, dim=3.2)

TotalSOCBudget    <- mbind(TotalSOCBudget,
                           setNames(ManureInput - CarbonInTot[,,"manure"], "manure_decay"),
                           setNames(ResidueInput[,,"ag"] - CarbonInTot[,,"ag"], "ag_decay"),
                           setNames(ResidueInput[,,"bg"] - CarbonInTot[,,"bg"], "bg_decay"))

SOCIn             <- dimSums(CarbonInTot, dim=3)
SOCtransfer       <- CarbonToEff[,,"crop"] 
SOCPrev           <- dimSums(grepSpaceTime(setYears(
                       SoilCarbonOut[,1,"actualstate"][,,"crop"]*Landuse[,1,"crop"], year)), dim=3)
SOCLoss           <- SOCPrev - SOCtot[,,"crop"] + SOCtransfer + SOCIn

TotalSOCBudget    <- mbind(TotalSOCBudget,
                           setNames(SOCLoss, "soc_decay"))

write.magpie(TotalSOCBudget, paste0(outputdir,"TotalSOCBudget.cs3"))

@@

```{r}

### 2020-12-14 ResultNotebooks/results_SOCmaps.Rmd
Flow figure update

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

rev <- "rev0.11"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

@@

library(ggplot2)

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000

SoilCarbon <- SoilCarbon[,findset("past"),]
Landuse    <- Landuse[,findset("past"),]

Plot cellular maps

```{r plot density maps}

@@

# png(paste0(outputdir,"CDens_2010.png"), width = 1280, height = 720, res = 108)
# luplot::plotmap2(cropland_dens[,"y2010",], legend_range = c(0,300), lowcol = cols[1], midcol = cols[4], highcol = cols[7], ncol=7, legend_discrete = TRUE)
# dev.off()
# 
# # png(paste0(outputdir,"CShare_1965.png"),width = 1280, height = 720, res = 108)
# # luplot::plotmap(cropland_share[,"y1965",], legend_range = c(0,2), legend_colours = cols, main="C_share on Cropland 1965")
# # dev.off()
# 
# png(paste0(outputdir,"CShare_2010.png"), width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_share[,"y2010",], legend_range = c(0,2), legend_colours = cols, main="Stock Change Factor on Cropland 2010")
# dev.off()
# 
# # png(paste0(outputdir,"CIncrease_1965.png"),width = 1280, height = 720, res = 108)
# # luplot::plotmap(cropland_increase[,"y1965",], legend_range = c(-80,80), legend_colours = cols, main="Absoulte C change on Cropland 1965")
# # dev.off()
# 
# png(paste0(outputdir,"CIncrease_2010.png"),width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_increase[,"y2010",], legend_range = c(-80,80), legend_colours = cols, legend_title = "tC/ha", main="Absoulte C change on Cropland 2010")
# dev.off()

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

>>>>

```{r load}
library(magclass)
library(madrat)
library(magpiesets)

rev <- "rev16"

@@

library(reshape2)

years <- seq(1975,2010,1)

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,years,][,,"state",pmatch=TRUE], dim=3.3)* Landuse[,years,], dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000

@@

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

### 2020-12-14 SOCbudgetPaper/SOCbudget.tex
Flow figure update

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t-1,sub,lu} + (SOC^{\mathrm{eq}}_{i,t,sub,lu} - SOC_{i,t-1,sub,lu}) \cdot k_{i,t,sub,lu} \cdot 1\unit{a}.
\label{eq:SOCstate}
\end{equation}

@@

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t-1,sub,lu} - \underbrace{SOC_{i,t-1,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}_{\text{outflow}} + \overbrace{SOC^{\mathrm{eq}}_{i,t,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}^{\text{input (using equation (1))}}.
\label{eq:steadystate2budget}
\end{equation}

@@

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 03:39:00 2020

>>>>

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t^*,sub,lu} + (SOC^{\mathrm{eq}}_{i,t,sub,lu} - SOC_{i,t^*,sub,lu}) \cdot k_{i,t,sub,lu} \cdot 1\unit{a}.
\label{eq:SOCstate}
\end{equation}

@@

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t^*,sub,lu} - \underbrace{SOC_{i,t^*,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}_{\text{outflow}} + \overbrace{SOC^{\mathrm{eq}}_{i,t,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}^{\text{input (using equation (1))}}.
\label{eq:steadystate2budget}
\end{equation}

@@

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 05:34:22 2020

### 2020-12-14 SOCbudgetPaper/methods.Rmd
Flow figure update

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t-1,sub,lu} + (SOC^{\mathrm{eq}}_{i,t,sub,lu} - SOC_{i,t-1,sub,lu}) \cdot k_{i,t,sub,lu} \cdot 1\unit{a}.
(\#eq:SOCstate)
\end{equation}

@@

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t-1,sub,lu} - \underbrace{SOC_{i,t-1,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}_{\text{outflow}} + \overbrace{SOC^{\mathrm{eq}}_{i,t,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}^{\text{input (using equation (1))}}.
(\#eq:steadystate2budget)
\end{equation}

>>>>

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t^*,sub,lu} + (SOC^{\mathrm{eq}}_{i,t,sub,lu} - SOC_{i,t^*,sub,lu}) \cdot k_{i,t,sub,lu} \cdot 1\unit{a}.
(\#eq:SOCstate)
\end{equation}

@@

\begin{equation}
SOC_{i,t,sub,lu} = SOC_{i,t^*,sub,lu} - \underbrace{SOC_{i,t^*,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}_{\text{outflow}} + \overbrace{SOC^{\mathrm{eq}}_{i,t,sub,lu} \cdot k_{i,t,sub,lu} \cdot 1\unit{a}}^{\text{input (using equation (1))}}.
(\#eq:steadystate2budget)
\end{equation}
